Basics of Hardware Cache Optimization

### 2017-05-31 tex/types.tex
Remove obsolete comment
Replace two tikzpicture environments with \tikz
I think these uses of \tikz are a shorter and semantically identical
alternative to using the tikzpicture environment.  See the second
paragraph of section 2.3 "Straight Path Construction" (page 31) of the
TikZ and PGF manual (version 3.0.1a).
Make KiB tick typesetting more automatic

% XXX: hacks!  Explicit placement specifier without `t` (top) to prevent the figure from
% interrupting the source code listing.
\begin{figure}%[hbp]
   \centering
   \begin{tikzpicture}
      \datavisualization[%
         scientific axes=clean,
         x axis={%
            logarithmic,
            ticks={major={
               /pgf/number format/int detect,
               at={
                  2048 as 2, 8192 as 8, 32768 as \textbf{32}, 131072 as 128,
                  524288 as \textbf{512}, 2097152 as \pgfmathprintnumber{2048},
                  8388608 as \pgfmathprintnumber{8192},
                  33554432 as \pgfmathprintnumber{32768},
                  134217728 as \pgfmathprintnumber{131072},
                  % $128\cdot 2^{10}$}}},
                  % $2^{17}$}}},
            }}},
            grid={at={32768, 524288}},
            label={Array Size (KiB)},
            length=0.8\textwidth},
         y axis={include value=0, label={Cycles / Iteration}, length=6cm, grid=at ticks},
         visualize as scatter,
         scatter={style={mark=*, mark options={scale=.65}}}]
         data [read from file=access-times/access-times.csv, separator=\space];
   \end{tikzpicture}
   % \caption{Access Times for Random Reads (\Cref{lst:access-times})}
   \caption{Access Times for Random Reads}
   \label{fig:access-times}
\end{figure}

>>>>

% Perform an integer division by 1024 on an argument in the format (scientific notation)
% provided to the `tick typesetting` key.  Amazing.  This took me half a day to write.
% See page 805 of the TikZ and PGF manual (version 3.0.1a).  We don't use
% `\pgfmathprintnumberto` because its result is in math mode, e.g. `$42$`.
% `pgfmathfloatparsenumber` allows arbitrary precision.
\def\kibtypesetter#1{%
   % \pgfmathprintnumberto[int trunc,1000 sep={}]{#1}{\a}
   \pgfmathfloatparsenumber{#1}%
   \pgfmathfloattoint{\pgfmathresult}%
   \pgfmathsetmacro{\a}{\pgfmathresult}%
   \newcount\b%
   \b=\number\a%
   \divide\b by 1024%
   \pgfmathprintnumber{\the\b}%
}

\def\emphkibtypesetter#1{%
   \ensuremath{\mathbf{\kibtypesetter{#1}}}%
}

% % This uses floating-point division.
% \def\kibtypesetter#1{%
%    \pgfmathparse{#1/1024}%
%    % \pgfmathdivide{#1}{1024}%
%    % \pgfmathdiv{#1}{1024}%
%    \pgfmathprintnumber{\pgfmathresult}%
% }

\tikzdatavisualizationset{
   array size vs cycles plot/.style={
      scientific axes=clean,
      x axis={
         logarithmic,
         ticks={
            /pgf/number format/int detect,
            major={
               tick typesetter/.code=\kibtypesetter{####1},
               at={
                  2048, 8192, 131072, 2097152, 8388608, 33554432, 134217728,
                  32768 as \emphkibtypesetter{32768},
                  524288 as \emphkibtypesetter{524288},
                  % 32768 as [style={font=\bfseries}],
                  % 32768 as \textbf{\kibtypesetter{32768}},
                  % 32768 as \ensuremath{\mathbf{\kibtypesetter{32768}}},
                  % 32768 as [tick typesetter/.code=\emphkibtypesetter],
               },
            },
            % minor={
               % style=black, tick text at low,
               % tick typesetter/.code={\kibtypesetter{##1}},
               % at={2048, 8192, 131072, 2097152, 8388608, 33554432, 134217728},
            % },
            minor at={4096, 16384, 65536, 262144, 1048576, 4194304, 16777216, 67108864},
         },
         grid={at={32768, 524288}},
         label={Array Size (KiB)},
         length=0.8\textwidth,
      },
      y axis={include value=0, label={Cycles / Iteration}, length=6cm, grid=at ticks},
      visualize as scatter,
      scatter={style={mark=*, mark options={scale=.65}}},
   },
}

\begin{figure}
   \centering
   \tikz \datavisualization[array size vs cycles plot]
      data [read from file=access-times/access-times.csv, separator=\space];
   % \caption{Access Times for Random Reads (\Cref{lst:access-times})}
   \caption{Access Times for Random Reads}
   \label{fig:access-times}
\end{figure}
